---
title: "Neural Net"
output: html_document
---
```{r}
library(readxl)
library(forecast)
data <- read_excel("/Users/nicklasschmidt/Downloads/Master thesis/Dataset/EnergyDataset1.xlsx", 
    col_types = c("date", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric"))
data = na.omit(data)
str(data)
```

```{r}
library(forecast)
set.seed(1337)
Year = 2021
Month = c("February", "July", "September", "December")
MonthNumber = c(32, 182, 244, 335)

for(MonthVariables in 1:4){
# First we convert dataset into a time series object
Ts = ts(data[,2:2], start = c(2017,1), frequency = 365 )

#Subsetting train and test data using window()function 
month2019train = window(Ts, end = c(Year, MonthNumber[MonthVariables]))
month2019test = window(Ts, start = c(Year, MonthNumber[MonthVariables]))

#Models estimating.
var.model= nnetar(month2019train, lambda=0, size = 20)

#Forecasting for 1-28 days 
model1dec2019=forecast(var.model, h=1)
model7dec2019=forecast(var.model, h=7)
model14dec2019=forecast(var.model, h=14)
model21dec2019=forecast(var.model, h=21)
model28dec2019=forecast(var.model, h=28)

# Accuracy TABLE
decna1=accuracy(model1dec2019, month2019test)[2,1:6]
decna7=accuracy(model7dec2019, month2019test)[2,1:6]
decna14=accuracy(model14dec2019, month2019test)[2,1:6]
decna21=accuracy(model21dec2019, month2019test)[2,1:6]
decna28=accuracy(model28dec2019, month2019test)[2,1:6]

accuracytable = rbind(decna1,decna7,decna14,decna21,decna28)
#plot table
naivetable = cbind(Month[MonthVariables],accuracytable)
rownames(naivetable) = c("Point","7 days","14 days","21 days","28 days")

if (MonthVariables == 1) {FebruaryTable = naivetable}
if (MonthVariables == 2) {JulyTable = naivetable}
if (MonthVariables == 3) {SeptemberTable = naivetable}
if (MonthVariables == 4) {DecemberTable = naivetable}

naivetsplot = window(Ts, start = c(Year, 1),end = c(Year + 1,1))
prettyplot = autoplot(naivetsplot, xlab = "Year", ylab = "Electricity price in DK1 area", main="Vector AR plot, h=1,7,14,21,28")+autolayer(model28dec2019, series = "28 Days", PI = FALSE, size = 1)+autolayer(model21dec2019, series = "21 Days", PI = FALSE, size = 1)+autolayer(model14dec2019, series = "14 Days", PI = FALSE, size = 1)+autolayer(model7dec2019, series = "7 Days", PI = FALSE, size = 1)+autolayer(model1dec2019, series = "Days point", PI = FALSE, size = 1)
assign(paste0("prettyplot",MonthVariables),prettyplot)

}
#subset DK1 
FebruaryTable[,c(3,4,7)]
JulyTable[,c(3,4,7)]
SeptemberTable[,c(3,4,7)]
DecemberTable[,c(3,4,7)]

RMSEtable = cbind(as.numeric(FebruaryTable[,3]),as.numeric(JulyTable[,3]),as.numeric(SeptemberTable[,3]),as.numeric(DecemberTable[,3]))
rownames(RMSEtable) = c("Point","7 days","14 days","21 days","28 days")
colnames(RMSEtable) = c("February","July","September","December")
AverageRMSEtable = rowMeans(RMSEtable)
AverageRMSEtable

MAEtable = cbind(as.numeric(FebruaryTable[,4]),as.numeric(JulyTable[,4]),as.numeric(SeptemberTable[,4]),as.numeric(DecemberTable[,4]))
rownames(MAEtable) = c("Point","7 days","14 days","21 days","28 days")
colnames(MAEtable) = c("February","July","September","December")
AverageMAEtable = rowMeans(MAEtable)
AverageMAEtable

MASEtable = cbind(as.numeric(FebruaryTable[,7]),as.numeric(JulyTable[,7]),as.numeric(SeptemberTable[,7]),as.numeric(DecemberTable[,7]))
rownames(MASEtable) = c("Point","7 days","14 days","21 days","28 days")
colnames(MASEtable) = c("February","July","September","December")
AverageMASEtable = rowMeans(MASEtable)
AverageMASEtable

prettyplot1
prettyplot2
prettyplot3
prettyplot4
``````
 
# with logaritmit transformation
```{r}
library(forecast)
set.seed(1337)
Year = 2021
Month = c("February", "July", "September", "December")
MonthNumber = c(32, 182, 244, 335)

for(MonthVariables in 1:4){
# First we convert dataset into a time series object
Ts = ts(data[,2:2], start = c(2017,1), frequency = 365 )


TsDiff = BoxCox(Ts,BoxCox.lambda(Ts))


#Subsetting train and test data using window()function 
month2019train = window(TsDiff, end = c(Year, MonthNumber[MonthVariables]))
month2019test = window(TsDiff, start = c(Year, MonthNumber[MonthVariables]), end=c(Year, MonthNumber[MonthVariables]))

#Models estimating.
var.model= nnetar(month2019train, lambda=0, size = 20)


#Forecasting for 1-28 days 
model1dec2019=forecast(var.model, h=1)
model7dec2019=forecast(var.model, h=7)
model14dec2019=forecast(var.model, h=14)
model21dec2019=forecast(var.model, h=21)
model28dec2019=forecast(var.model, h=28)


# Accuracy TABLE
decna1=accuracy(InvBoxCox(model1dec2019$mean,BoxCox.lambda(Ts)), InvBoxCox(month2019test,BoxCox.lambda(Ts)))[2:3]
decna7=accuracy(InvBoxCox(model7dec2019$mean,BoxCox.lambda(Ts)), InvBoxCox(month2019test,BoxCox.lambda(Ts)))[2:3]
decna14=accuracy(InvBoxCox(model14dec2019$mean,BoxCox.lambda(Ts)), InvBoxCox(month2019test,BoxCox.lambda(Ts)))[2:3]
decna21=accuracy(InvBoxCox(model21dec2019$mean,BoxCox.lambda(Ts)), InvBoxCox(month2019test,BoxCox.lambda(Ts)))[2:3]
decna28=accuracy(InvBoxCox(model28dec2019$mean,BoxCox.lambda(Ts)),InvBoxCox(month2019test,BoxCox.lambda(Ts)))[2:3]


accuracytable = rbind(decna1,decna7,decna14,decna21,decna28)
#plot table
naivetable = cbind(Month[MonthVariables],accuracytable)
rownames(naivetable) = c("Point","7 days","14 days","21 days","28 days")

if (MonthVariables == 1) {FebruaryTable = naivetable}
if (MonthVariables == 2) {JulyTable = naivetable}
if (MonthVariables == 3) {SeptemberTable = naivetable}
if (MonthVariables == 4) {DecemberTable = naivetable}

#naivetsplot = window(Ts, start = c(Year, 1),end = c(Year + 1,1))

#prettyplot = autoplot(naivetsplot, xlab = "Year", ylab = "Electricity price in DK1 area", main="Vector AR plot, h=1,7,14,21,28")+autolayer(model28dec2019$mean,BoxCox.lambda(Ts)), series = "28 Days", PI = FALSE, size = 1)+autolayer(model21dec2019$mean,BoxCox.lambda(Ts)), series = "21 Days", PI = FALSE, size = 1)+autolayer(InvBoxCox(model14dec2019$mean,BoxCox.lambda(Ts)), series = "14 Days", PI = FALSE, size = 1)+autolayer(InvBoxCox(model7dec2019$mean,BoxCox.lambda(Ts)), series = "7 Days", PI = FALSE, size = 1)+autolayer(InvBoxCox(model1dec2019$mean,BoxCox.lambda(Ts)), series = "Days point", PI = FALSE, size = 1)
#assign(paste0("prettyplot",MonthVariables),prettyplot)

}
#subset DK1 
FebruaryTable[,c(2,3)]
JulyTable[,c(2,3)]
SeptemberTable[,c(2,3)]
DecemberTable[,c(2,3)]

RMSEtable = cbind(as.numeric(FebruaryTable[,2]),as.numeric(JulyTable[,2]),as.numeric(SeptemberTable[,2]),as.numeric(DecemberTable[,2]))
rownames(RMSEtable) = c("Point","7 days","14 days","21 days","28 days")
colnames(RMSEtable) = c("February","July","September","December")
AverageRMSEtable = rowMeans(RMSEtable)
AverageRMSEtable

MAEtable = cbind(as.numeric(FebruaryTable[,3]),as.numeric(JulyTable[,3]),as.numeric(SeptemberTable[,3]),as.numeric(DecemberTable[,3]))
rownames(MAEtable) = c("Point","7 days","14 days","21 days","28 days")
colnames(MAEtable) = c("February","July","September","December")
AverageMAEtable = rowMeans(MAEtable)
AverageMAEtable


#prettyplot1
#prettyplot2
#prettyplot3
#prettyplot4

```

```{r}
library(data.table)
prettyplot = autoplot(naivetsplot, xlab = "Year", ylab = "Electricity price in DK1 area", main="Vector AR plot, h=1,7,14,21,28")+autolayer(model7dec2019ts, series = "28 Days", PI = FALSE, size = 1)

#autoplot(model1dec2019=InvBoxCox(model1dec2019$mean,BoxCox.lambda(Ts)))
model7dec2019=InvBoxCox(model7dec2019$mean,BoxCox.lambda(Ts))
transpose(model7dec2019)
model7dec2019ts = ts(model7dec2019, start = c(2019,355), frequency = 365)

plot(model1dec2019ts)

```


